Improving Software Maintainability through Automated Refactoring of Code Clones

### 2020-01-10 ecoop/paper.tex
Updates from Overleaf

\subsubsection{Maintainability metrics} \label{sec:metrics}
CR measures the impact on maintainability metrics of refactoring source code for each clone class that is refactored. These metrics are from Heitlager et al.~\cite{heitlager2007practical}. For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.

>>>>

\subsubsection{Selected metrics} \label{sec:metrics}
CR measures the impact on maintainability metrics of refactoring source code for each clone class that is refactored. These metrics are from Heitlager et al.~\cite{heitlager2007practical}. For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
